Survey procedure and participant training

### 2023-03-21 paper/supplementary/lineups.Rmd
supplementary material processed

  # Downloaded data
d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))

@@

The detection rate is considered for each lineup. The detection rates for group A were less varied than the detection rates for the lineups seen by group B. Fig. \ref{fig:pdetection-group} shows the distribution using a boxplot. This shows the median value for detection rate was extremely similar.

```{r pdetection-group}
plots %>% ggplot(aes(x = group, y = pdetect)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  ylab("Detection rate") + 
  ylim(c(0,1))
```

The overall detection rate is considered for each trend model in Fig. \ref{fig:pdetect-trend}.
The detection rates for the NW-SE trend model was less varied than the detection rates for the Three Cities and All Cities trends. Fig. \ref{fig:pdetection-group} shows the distribution using a boxplot. This shows the distributions of the rates do not overlap for NW-SE and Three Cities trends, the Three cities range was larger, but the median was much higher for the NW-SE trend. The All Cities trend model distribution overlaps with the NW-SE and All Cities trends.

```{r pdetect-trend}
plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
  geom_boxplot() + 
  scale_fill_manual(values = trend_colours) +
  geom_jitter(width = 0.1) +
  ylab("Detection rate") + 
  ylim(c(0,1)) 
```

The boxplots in Fig. \ref{fig:pdetection-type} contrast the distribution of the detection rates for eah type of display.
The detection rates across the lineups was less varied for the hexagon display. There was a large difference in the medians for the types of displays.
Without considering the relationship for each lineup, the hexagon lineup display allowed the participants to achieve higher detection rates.

```{r pdetection-type}
plots %>% ggplot(aes(x = type, y = pdetect, fill = type)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  scale_fill_manual(values = type_colours) +
  ylab("Detection rate") + 
  ylim(c(0,1))
```

@@

Each lineup had twelve map displays, this gave participants the choice of any plot, and the choice to not provide a response. this non-reponse is indicated by 0.
The choices made by participants are displayed in Fig. \ref{fig:choices}. The height of each orange lollipop indiates the proportion of participants that selected the map display of real data, they represent the correct choices.
The green lollipops show the proportion of participants that selected the incorrect displays in each lineup.

The proportion of choices are also presented separately for each trend model in Table. \ref{tab:choice-nwse}, Table. \ref{tab:choice-three}, and  Table. \ref{tab:choice-all}.
The correct map display in lineups with a North West to South East trend was chosen correctly with much greater frequency. 
In the lineups of All Cities displays, participants were misled by the choropleth display, but not the hexagon display for all except (2). 
All of Three Cities displays, except (4), were detected in the hexagon display. All except one lineup had at least one participant select the correct map in the lineup as shown in Fig. \ref{fig:choices}.

```{r choices, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup. The points coloured orange show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6, results = "asis"}
d %>% 
  count(type, trend, choice, replicate, choice, detect_f) %>% 
  group_by(type, trend, replicate) %>% 
  mutate(prop = n/sum(n)) %>% 
  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
  mutate(bottom = 0) %>% 
  ggplot() + 
  geom_point(aes(x = choice, y = prop, color = detect_f), size = 3) + 
  geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +
  facet_grid(repl ~ trend, 
    drop = TRUE, as.table = TRUE, scales = "free_y") +
  labs(x = "Choice of plot in lineup", y = "Amount of choices") +
  scale_colour_manual(values = detect_colours) +
  scale_x_continuous(breaks = seq(from = 0, to = 12)) +
  scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
  theme(legend.position = "bottom") + 
  guides(colour = FALSE, fill = FALSE) +
  theme(strip.text.y = element_text(angle = 0))
```

@@

## North West - South East

@@

## All Cities

### Replicate 1

@@

### Replicate 2

@@

### Replicate 3

@@

### Replicate 4

@@

## Three Cities

### Replicate 1

@@

### Replicate 2

@@

### Replicate 3

@@

## North West to South East Geographic Trend

### Replicate 1

@@

```{r nwse-hex2, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 12 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_geo.png")))
```

### Replicate 2

@@

```{r nwse-hex3, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 3 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_geo.png")))
```

### Replicate 3

@@

```{r nwse-hex5, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 4 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_geo.png")))
```

### Replicate 4

>>>>

  # Downloaded data
d <- read_xlsx("../data/experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))

@@

The detection rate is considered for each lineup. The detection rates for group A were less varied than the detection rates for the lineups seen by group B. Fig. 1 shows the distribution using a boxplot. This shows the median value for detection rate was extremely similar.

```{r pdetection-group, fig.cap="Comparison of performance of groups A and B."}
plots %>% ggplot(aes(x = group, y = pdetect)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  ylab("Detection rate") + 
  ylim(c(0,1))
```

The overall detection rate is considered for each trend model in Fig. 2.
The detection rates for the NW-SE trend model was less varied than the detection rates for the Three Cities and All Cities trends. This shows the distributions of the rates do not overlap for NW-SE and Three Cities trends, the Three cities range was larger, but the median was much higher for the NW-SE trend. The All Cities trend model distribution overlaps with the NW-SE and All Cities trends.

```{r pdetect-trend, fig.cap="Comparison of performance across trend models."}
plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
  geom_boxplot() + 
  scale_fill_manual(values = trend_colours) +
  geom_jitter(width = 0.1) +
  ylab("Detection rate") + 
  ylim(c(0,1)) 
```

The boxplots in Fig. 3 contrast the distribution of the detection rates for each type of display.
The detection rates across the lineups was less varied for the hexagon display. There was a large difference in the medians for the types of displays.
Without considering the relationship for each lineup, the hexagon lineup display allowed the participants to achieve higher detection rates.

```{r pdetection-type, fig.cap="Comparison of performance across display types."}
plots %>% ggplot(aes(x = type, y = pdetect, fill = type)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  scale_fill_manual(values = type_colours) +
  ylab("Detection rate") + 
  ylim(c(0,1))
```

@@

Each lineup had twelve map displays, this gave participants the choice of any plot, and the choice to not provide a response. this non-reponse is indicated by 0.
The choices made by participants are displayed in Fig. 4. The height of each orange lollipop indiates the proportion of participants that selected the map display of real data, they represent the correct choices.
The green lollipops show the proportion of participants that selected the incorrect displays in each lineup.

The proportion of choices are also presented separately for each trend model in Table.
The correct map display in lineups with a North West to South East trend was chosen correctly with much greater frequency. 
In the lineups of All Cities displays, participants were misled by the choropleth display, but not the hexagon display for all except (2). 
All of Three Cities displays, except (4), were detected in the hexagon display. All except one lineup had at least one participant select the correct map in the lineup as shown in Fig. 4.

```{r choices, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup. The points coloured orange show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width = 6,}
d %>% 
  count(type, trend, choice, replicate, choice, detect_f) %>% 
  group_by(type, trend, replicate) %>% 
  mutate(prop = n/sum(n)) %>% 
  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
  mutate(bottom = 0) %>% 
  ggplot() + 
  geom_point(aes(x = choice, y = prop, color = detect_f), size = 3) + 
  geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +
  facet_grid(repl ~ trend, 
    drop = TRUE, as.table = TRUE, scales = "free_y") +
  labs(x = "Choice of plot in lineup", y = "Amount of choices") +
  scale_colour_manual(values = detect_colours) +
  scale_x_continuous(breaks = seq(from = 0, to = 12)) +
  scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
  theme(legend.position = "bottom") + 
  guides(colour = FALSE, fill = FALSE) +
  theme(strip.text.y = element_text(angle = 0))
```

@@

<!-- ## North West - South East-->

@@

<!-- ## All Cities

### Replicate 1-->

@@

<!-- ### Replicate 2-->

@@

<!-- ### Replicate 3-->

@@

<!--### Replicate 4-->

@@

<!--## Three Cities

### Replicate 1-->

@@

<!--### Replicate 2-->

@@

<!--### Replicate 3-->

@@

<!--## North West to South East Geographic Trend

### Replicate 1-->

@@

```{r nwse-hex2, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 12 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_hex.png")))
```

<!--### Replicate 2-->

@@

```{r nwse-hex3, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 3 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_hex.png")))
```

<!--### Replicate 3-->

@@

```{r nwse-hex5, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 4 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_hex.png")))
```

<!--### Replicate 4-->

### 2023-03-21 paper/supplementary/survey_procedures.Rmd
supplementary material processed

Participants were recruited via advertising on the Figure-Eight crowdsource platform.
Choosing the task from the list directed all potential participants to the page of instructions.
This page contained written instructions and is shown in Fig. \ref{fig:instruct}.

```{r instruct, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_instruct.png")))
```

@@

The participants were trained using three displays. There were relatively simple lineups, they are displayed in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.

```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_training1.png")))
```

```{r training2, results = "asis", fig.cap = "The training lineups of hexagon tile maps.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_training2.png")))
```

@@

The demographic and consent page of the `shinydashboard` web application are displayed in Fig. \ref{fig:survey-demogs}. Two example lineups are shown, one choropleth map lineup in Fig. \ref{fig:survey-choro} and one heaxgon tile map lineup in Fig. \ref{fig:survey-hex}.

```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_demogs.png")))
```

```{r survey-choro, results = "asis", fig.cap = "An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_choro.png")))
```

```{r survey-hex, results = "asis", fig.cap = "An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_hex.png")))
```

>>>>

Participants were recruited via advertising on the Figure-Eight crowdsource platform.
Choosing the task from the list directed all potential participants to the page of instructions.
This page contained written instructions and is shown below.

```{r instruct, results = "asis", fig.cap = "Introductory information provided to participants."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_instruct.png")))
```

@@

The participants were trained using simple lineups of three displays as shown in Figs. 2, 3.

```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_training1.png")))
```

```{r training2, results = "asis", fig.cap = "The training lineups of hexagon tile maps."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_training2.png")))
```

@@

The demographic and consent page of the `shinydashboard` web application are displayed in Fig. 4. Two example lineups are shown, one choropleth map lineup in Fig. 5 and one heaxgon tile map lineup in Fig. 6.

```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_demogs.png")))
```

```{r survey-choro, results = "asis", fig.cap = "An example of the choropleth map lineup shown in the survey tab of the shinydashboard app."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_choro.png")))
```

```{r survey-hex, results = "asis", fig.cap = "An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_hex.png")))
```
